Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-23 Grassmannian_cells.tex
Notation change before Example 3.37

Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$. Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$. These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\CC$.

>>>>

%Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
